---
title: "Practical Exam"
author: "Alfe Kevin P. Gallo"
date: "2024-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1A. Find out, in a single command, which columns of warpbreaks are either numeric or 
integer. What are the data types of each column?
```{r}
data("warpbreaks")
#column "breaks" integer data types and both column "wool" and " tension" have character data types
```
2A.How many observations does it have?
```{r}

str(warpbreaks)
#54 observations
```
3A.s numeric a natural data type for the columns which are stored as such? Convert to 
integer when necessary.
```{r, error=TRUE}
integerwarpbreaks <- warpbreaks

integerwarpbreaks <- as.integer(warpbreaks)

integerwarpbreaks <- as.integer(warpbreaks$wool)

integerwarpbreaks <- as.integer(warpbreaks$tension)


```
4A. Error messages in R sometimes report the underlying type of an object rather than the user-level class. Derive from the following code and error message what the underlying type. Explain what is the error all about. Do not just copy the error 
message that was displayed.
```{r}
#there is an error that cannot b forced to become an integer because it is already an integer

```
1B. Read the complete file using readLines.
```{r}
exampleFile <- readLines("/cloud/project/PractExam/exampleFile.txt")
exampleFile

```
2B.  Separate the vector of lines into a vector containing comments and a vector containing the data. Hint: use grepl.
```{r}
vectorcomment <- exampleFile[grepl("//",exampleFile)]
vectorcomment

vectordata <-  exampleFile[grepl(";",exampleFile)]
vectordata
```
3B.